Evolution of pre-copulatory and post-copulatory inbreeding behaviour: a computational approach

### 2016-09-15 ms_pre_post.Rmd
Initial passage on constraints

>>>>

Our model assumed that allele values underlying tendency for polyandry, pre-copulatory inbreeding avoidance, and post-copulatory inbreeding avoidance were all initialised at zero (causing monandry, and random mating and fertilisation with respect to kinship), and phenotypes evolved simultaneously after initialisation. However, these initial conditions are likely to be atypical, as evolution of pre-copulatory and post-copulatory inbreeding avoidance from ancestral random mating and fertilisation is unlikely to occur simultaneously. Rather, initial evolution of one inbreeding strategy (e.g., pre-copulatory inbreeding avoidance) is more likely to occur in the absence of its complementary strategy (e.g., post-copulatory inbreeding avoidance) if the complementary strategy is evolutionarily constrained. Alternatively, initial evolution of one inbreeding strategy might occur in the context of an already established adaptive strategy for avoiding inbreeding.
